New lower bounds for Schur and weak Schur numbers

### 2021-09-22 article/abstract-JTO.tex
Add files via upload
Une proposition de l'abstract.

\documentclass[3p]{elsarticle}
\title{New lower bounds for Schur and weak Schur numbers}
\author{Romain Ageron, Paul Casteras, Thibaut Pellerin, Yann Portella}

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{dsfont}
\usepackage{MyMnSymbol}

\usepackage[english]{babel}
\usepackage[hyphens]{url}
\usepackage{hyperref}
\usepackage[utf8]{inputenc}
\usepackage{siunitx}
\usepackage{float}

\usepackage[table]{xcolor}
\usepackage{multirow}
\usepackage{nicematrix}

\renewcommand{\qedsymbol}{\(\square\)}

\newtheorem{definition}{Definition}[section]
\newtheorem{notation}[definition]{Notation}
\newtheorem{theorem}[definition]{Theorem}
\newtheorem{computational theorem}[definition]{Computational Theorem}
\newtheorem{corollary}[definition]{Corollary}
\newtheorem{remark}[definition]{Remark}
\newtheorem{proposition}[definition]{Proposition}

\newcommand{\WS}{\mathit{WS}}
\newcommand{\docarraystretch}{1.2}
\newcommand{\resetarraystretch}{\renewcommand{\arraystretch}{\docarraystretch}}
\resetarraystretch

@@

\begin{abstract}

@@

\end{abstract}

\maketitle

\input{introduction.tex}

\input{schur.tex}

\input{weakschur.tex}

\section{Conclusions and future work}

\qquad These new results come from an extension of Rowley's template-based approach for Ramsey graphs and 
Schur numbers which is relatively new. Therefore, we will not be surprised if lower bounds are later improved 
using better templates. Moreover, studying specifically \(S^+(n)\) and \(\WS^+(n)\) might be of interest as they
 are closely related to Schur and weak Schur numbers. In order to find new templates, algorithms based on 
randomness such as Monte-Carlo algorithms may prove to be very useful. This could be the subject of a future work.

\section{Acknowledgments}

\qquad We would first like to thank our professors, Joanna Tomasik and Arpad Rimmel, who guided and advised
us during the whole research and writing. We also would like to address warm thanks
to Fred Rowley who kindly answered our many questions and with who it was a pleasure to exchange. 
Last but not least, we would like to thank Marijn Heule for providing the backdoors used in the computation of the 
new lower bound for \(\WS(6)\).

\bibliography{biblio}
\bibliographystyle{elsarticle-num.bst}

\include{appendix.tex}

>>>>

\documentclass[12pt]{article}

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}

\newcommand{\WS}{\mathit{WS}}

@@

\textbf{INITIAL VERSION}

\smallskip

@@

\bigskip

\textbf{REVISED VERSION}

\smallskip

We provide one with new lower bounds for both Schur and weak Schur numbers exploiting a template-based approach for Schur and Ramsey numbers. These bounds for Schur are \(S(9) \geqslant 17\,803\) and \(S(10) \geqslant 60\,948\), while for weak Schur they are \(\WS(6) \geqslant 646\), \(\WS (9) \geqslant 22\,536\), and 
\(\WS (10) \geqslant 71\,256 \).

The enriched templates developed also allow us to explicit the growth rate for Schur,  weak Schur, and Ramsey numbers \(R_n(3)\).
